---
title: "Logistic Regression with Multivariate Statistics"
author: "Adrián Echeverría P."
output:
  rmdformats::material:
  html_document:
    keep_md: true
    suppress_warnings: true
    suppress_messages: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries:
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(corrplot)
library(MASS)
library(GGally)
library(CCA)
```

## Loading dataset:
```{r}
df <- read.csv('C:\\Users\\Usuario\\Desktop\\jm1.csv')
```

## Setting variables to numeric:

#### The defects column, which is the one we want to predict, is in String values. Therefore, we must switch it to binary (1 or 0).
```{r, warning=FALSE, message=FALSE}
df$defects[df$defects == 'true'] <- 1
df$defects[df$defects == 'false'] <- 0
df$uniq_Op = as.numeric(as.character(df$uniq_Op))
df$uniq_Opnd = as.numeric(as.character(df$uniq_Opnd))
df$total_Op = as.numeric(as.character(df$total_Op))
df$total_Opnd = as.numeric(as.character(df$total_Opnd))
df$branchCount = as.numeric(as.character(df$branchCount))
df$defects = as.numeric(as.character(df$defects))
```

### Verifying the contents of the dataset:
```{r}
head(df)
```

## Statistical behavior of each column.
```{r}
summary(df)
```

## Correlation plot:
```{r}
df2 <- df[,c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,22)]
correlations <- cor(df2)
corrplot(correlations, method="circle")
```

## Boxplots with subplots:

#### We analyze if there are any outliers and how many. Moreover, we observe the distribution between variables.
```{r}
par(mfrow=c(2,4))
for(i in 1:21) {
    boxplot(df[,i], main=names(df)[i])
}
```

## Fitting the model and printing the normality.

#### The more asterisks included in each result, the better. These are features that are interesting for the model.
```{r}
glm.fit <- glm(defects ~ loc+v.g.+ev.g.+iv.g.+n+v+l+d+i+e+b+t+lOCode+lOComment+lOBlank+locCodeAndComment+uniq_Op+uniq_Opnd+total_Op+branchCount+defects, data = df, family = binomial)
summary(glm.fit)
```

```{r}
df3 <- df[,c(1,7,13,17,21,22)]
pairs(df3, col=df3$defects)
```

## Confusion Matrix:
```{r}
glm.probs <- predict(glm.fit, type = "response")
glm.pred <- ifelse(glm.probs > 0.5, 1, 0)

defects <- df$defects
defects <- defects[1:(length(defects) - 5)]
defects_factor <- factor(defects, levels = c(0, 1))

table(glm.pred, defects_factor)
```

## Accuracy of the model:
```{r}
mean(glm.pred == defects_factor)
```